The limits of self commitment and private paternalism \thanks{}

### 2022-12-20 donde.tex
revision of text

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}}\right)^{\text{loan duration}}-1 
\end{align*}

>>>>

\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Appraised Value}_i}}{\text{loan duration}_i}\right)^{\text{loan duration}_i}-1 
\end{align*}
